CS182: NBA Scheduler

### 2015-10-28 proposal.tex
change tsp to traveling salesman problem explicitly

	\begin{enumerate}
		\item Some form of greedy next-best search in choosing the next game - choose the next game for a team that makes sure the $N$ games in $M$ nights constraint is met then perform arc consistency
		\item The minimizing distance problem for a specific team is classic CSP - could try to model this problem in form of A* and find a heuristic based on number of divisional games remaining (divisional games are regionally closer) - then rearrange schedule to fit that team's path. We could try to first accomplish this but the goal is to minimize the combined distance for every team traveled which will require outside research to see if this is even feasible
		\item Research online for other techniques that haven't been discussed in class - surprisingly this has been an issue well researched in the NFL but not the NBA (probably because that's a smaller problem with only 16 games), but perhaps we can gain some insights from reading papers optimizing their schedule
	\end{enumerate}

>>>>

	\begin{enumerate}
		\item Some form of greedy next-best search in choosing the next game - choose the next game for a team that makes sure the $N$ games in $M$ nights constraint is met then perform arc consistency
		\item The minimizing distance problem for a specific team is classic traveling salesman problem - could try to model this problem in form of A* and find a heuristic based on number of divisional games remaining (divisional games are regionally closer) - then rearrange schedule to fit that team's path. We could try to first accomplish this but the goal is to minimize the combined distance for every team traveled which will require outside research to see if this is even feasible
		\item Research online for other techniques that haven't been discussed in class - surprisingly this has been an issue well researched in the NFL but not the NBA (probably because that's a smaller problem with only 16 games), but perhaps we can gain some insights from reading papers optimizing their schedule
	\end{enumerate}
